---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(classdata)
head(ames)
View(ames)
colnames(ames)
```

The column names that we are working with are, 

"Parcel ID"             "Address"              
 [3] "Style"                 "Occupancy"            
 [5] "Sale Date"             "Sale Price"           
 [7] "Multi Sale"            "YearBuilt"            
 [9] "Acres"                 "TotalLivingArea (sf)" 
[11] "Bedrooms"              "FinishedBsmtArea (sf)"
[13] "LotArea(sf)"           "AC"                   
[15] "FirePlace"             "Neighborhood"


```{r}
library(ggplot2)

ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 500000, fill = "blue", color = "black") +
  labs(title = "Histogram of Sale Price",
       x = "Sale Price",
       y = "Frequency")
```

The vast majority of the observations fall in the same general range but there are a few huge outliers that are far more expensive then other observations. 

```{r}
ggplot(ames, aes(x = Bedrooms, y = `Sale Price`)) +
  geom_point(color = "blue", size = 1) +
  labs(title = "Scatterplot of Sale Price vs. Bedrooms",
       x = "Number of Bedrooms",
       y = "Sale Price")
```

There are huge outliers again that ruin the plot in visibility, but there is a rough correlation between having more bathrooms and a higher sales price. --> Emmet Doyle
