---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


library(classdata)
head(ames)
View(ames)
colnames(ames)

<<<<<<< HEAD
=======
The column names that we are working with are, 

"Parcel ID"             "Address"              
 [3] "Style"                 "Occupancy"            
 [5] "Sale Date"             "Sale Price"           
 [7] "Multi Sale"            "YearBuilt"            
 [9] "Acres"                 "TotalLivingArea (sf)" 
[11] "Bedrooms"              "FinishedBsmtArea (sf)"
[13] "LotArea(sf)"           "AC"                   
[15] "FirePlace"             "Neighborhood"


```{r}
library(ggplot2)

ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 500000, fill = "blue", color = "black") +
  labs(title = "Histogram of Sale Price",
       x = "Sale Price",
       y = "Frequency")
```

The vast majority of the observations fall in the same general range but there are a few huge outliers that are far more expensive then other observations. 


>>>>>>> d1ed39277a9342783dda08270db50865f80d216f

Sales Price to YearBuilt


```{r}
ggplot(ames, aes(x = `YearBuilt`)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Houses by Year Built",
       x = "Year Built", y = "Frequency") +
  xlim(1900, max(ames$YearBuilt))
```

The range of this data is from around 1900 to 2024. As the year gets more recent there are for the most part more houses that were built.


```{r}
ggplot(ames, aes(x = `YearBuilt`, y = `Sale Price`)) +
  geom_point(color = "blue", alpha = 0.6) +  
  labs(title = "Scatterplot of Sale Price vs Year Built",
       x = "Year Built", y = "Sale Price") + xlim(1900, max(ames$YearBuilt))
```
       
This variable contains the odd high outliers of Sales Price. It is hard to fully see the distribution with these outliers skewing the y axis.


```{r}
filtered_ames_data <- subset(ames, `Sale Price` < 500000)

ggplot(filtered_ames_data, aes(x = `YearBuilt`, y = `Sale Price`)) +
  geom_point(color = "blue", alpha = 0.6) +
  labs(title = "Scatterplot of Sale Price vs Year Built (Filtered)",
       x = "Year Built", y = "Sale Price") +
  xlim(1900, max(filtered_ames_data$YearBuilt))
```
  

This helps view the distribution of most sale prices compared to the year built. As the year gets more recent, the price generally goes up. - Kathryn Keck
  
